### 2017-07-14 architecture.tex
Filling in on Kyle comments

Safe collection policies are expressed on \NAMENS's managed
data via AWS Identity and Access Management (IAM) policies 
and S3 bucket policies.
A safe collection is described in CloudFormation templates, where 
CloudFormation provides a reproducible method for instantiating infrastructure
based on a standard JSON description. For example, it defines
the S3 bucket to be used as well as the secure connections
to the rest of the \NAME system.
\kyle{I dont understand exactly how CloudFormation describes the collection? Is
what I wrote correct?}
%This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

>>>>

Safe collection policies are expressed on \NAMENS's managed
data via AWS Identity and Access Management (IAM) policies 
and S3 bucket policies.
A safe collection is described in CloudFormation templates, where
CloudFormation provides a reproducible method for instantiating infrastructure
based on a standard JSON description. For example, it defines
the S3 bucket, bucket policies granting exclusive administrative privileges to a steward role,
and IAM policies granting appropriate privileges to cloud kotta worker machines to store analysis results.
%This allows safe-collection descriptions to be verifiable, reproducible, and shareable.
